Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-06-09 sec_summary.tex
update on sec6

ALICE has measured the $p_{\mathrm T}$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV at the Large Hadron Collider. The spectrum of the ridge yield has been measured in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class. The result has been compared with CMS measurement and shown that the results are compatible. Further understandings of the correlations in small system have been tried by studying the ridge yield in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$. The ridge yield spectrum with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$.) shows enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases. The results have been compared with PYTHIA8 string shoving calculation, showing comparable enhancement as data.

>>>>

ALICE has measured the $p_{\mathrm T}$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV at the Large Hadron Collider. The spectrum of the ridge yield has been measured in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class. The result has been compared with CMS measurement and shown that the results are compatible. The PYTHIA8 string shoving has quantitatively estimated the spectrum while PYTHIA8 default shows zero yield. Further understandings of the correlations in small system have been attempted by studying the ridge yield in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$. The ridge yield spectrum with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$.) has shown the enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases. The results have been compared with PYTHIA8 string shoving calculation, showing the enhancement while underestimating the absolute ridge yield.
